%-------------------------
% Resume in Latex
% Author : Abhishek Arya
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% Adjust spacing between sections
\usepackage{setspace}
\setlength{\parskip}{0.5em}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Improve spacing for better readability
\linespread{1.05}
\setlength{\itemsep}{0.2em}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\fontsize{8.6}{10.32}\selectfont{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\fontsize{10}{12}\selectfont #2} \\
      \vspace{2pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.2em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\fontsize{24}{28.8}\selectfont \scshape Abhishek Arya} \\ \vspace{8pt}
    \fontsize{10}{12}{\selectfont
    \href{tel:+91-9205967162}{\underline{+91-9205967162}} \hspace{0.5em}$|$\hspace{0.5em}
    \href{mailto:abhishekarya102@gmail.com}{\underline{abhishekarya102@gmail.com}} \hspace{0.5em}$|$\hspace{0.5em} 
    \href{https://www.abhishekarya.com}{\underline{abhishekarya.com}} \hspace{0.5em}$|$\hspace{0.5em}
    \href{https://linkedin.com/in/abhishekarya-1}{\underline{linkedin.com/in/abhishekarya-1}}
    }
\end{center}
\vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Senior Software Engineer}{\textbf{Jul 2024 -- Present}}
      {UKG (Ultimate Kronos Group)}{Noida, India}
      \resumeItemListStart
        \resumeItem{Designing GitHub Actions workflows to automate UI and Integrations tests for a variety of test frameworks like Selenium, NUnit, Nightwatch JS, optimizing CI/CD efficiency and reducing manual effort.}
        \resumeItem{Building cross-platform reusable GitHub Actions in TypeScript for test execution, environment setup, and reporting, cutting workflow complexity and improving reusability.}
        \resumeItem{Integrated observability into GitHub Actions using OpenTelemetry, Jaeger, Datadog, and Splunk, enhancing traceability, logging, and metrics collection leading to better monitoring and alerting.}
        \resumeItem{Ideated and led the implementation of test execution in headless mode on Linux runners, cutting execution times by 30\% while maintaining test pass rates.}
        \resumeItem{The workflows and actions are used by ~30 core product teams across the organization as the primary test execution pipeline, reducing dependency on existing CI/CD tool (JetBrains TeamCity) and saving licensing costs by 40\%.}
    \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{\textbf{Jan 2023 -- Jul 2024}}
      {TCS (Tata Consultancy Services), Client - Macy's Inc.}{Noida, India}
      \resumeItemListStart
        \resumeItem{Developed and modernized critical platforms, including ad management, web analytics, and vendor portal, migrating 30+ applications to a cloud-based microservices architecture using Java 21, Spring Boot 3, and Spring Batch.}
        \resumeItem{Converted a supply chain legacy monolith to ~8 microservices with zero performance loss, implemented reactive programming with WebFlux and R2DBC for asynchronous business logic, JWT-based authentication with Spring Security, and integrated AWS SNS and Kafka for real-time notifications.}
        \resumeItem{Implemented batch job processing and scheduling pipelines using Spring Cloud Data Flow as the admin panel for the new application.}
        \resumeItem{Led the migration of a legacy key-value store (Oracle Berkeley DB) to Google Memorystore Redis, designed schema and developed code to migrate.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Dec 2020 -- Dec 2022}}
      {TCS (Tata Consultancy Services), Client - Safeway Inc.}{Remote, India}
      \resumeItemListStart
        \resumeItem{Migrated 10+ legacy applications, replacing mainframe systems and a third-party gateway with a cloud-based microservices architecture using Java Spring Boot, ensuring 99.99\% uptime and 30\% faster response times.}
        \resumeItem{Deployed ~20 microservices and the gateway application to Microsoft Azure with minimal downtime, reducing infrastructure costs by 40\% and improving system throughput by 20\%, while supporting 1000+ mission-critical requests per minute across 22 locations across North America.}
        \resumeItem{Optimized Jenkins CI/CD pipeline by introducing layered Docker images for the application, slashing build and deployment times by 75\% and improved monitoring with Prometheus and Grafana Dashboard for robust telemetry.}
        \resumeItem{Resolved critical performance and bottleneck issues, reducing recurring incidents by 80\%; developed a SonarQube report automation tool for stakeholders, enhancing code quality tracking.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Galgotias University}{Greater Noida, India}
    {Bachelor of Technology (B.Tech) in Computer Science and Engineering (CSE)}{\textbf{ 2016 -- 2020}}
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Programming}{\fontsize{9.5}{11}\selectfont: C, C++, Python, JavaScript, TypeScript, Java, Go, Bash } \\
     \textbf{Frameworks}{\fontsize{9.5}{11}\selectfont: J2EE, Web MVC, Spring Boot, Data JPA, Hibernate ORM, Spring Cloud, Batch, Reactive, JUnit, FastAPI, Node.js, React } \\
     \textbf{Tools}{\fontsize{9.5}{11}\selectfont: MySQL, Redis, MongoDB, Azure, GCP, AWS, ActiveMQ, Kafka, Git, Docker, Kubernetes, GitHub Actions, Jenkins, Linux} \\
     \textbf{AI}{\fontsize{9.5}{11}\selectfont: Ollama, LLM RAG, MCP}
    }
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cache-me-if-you-can!} $|$ \emph{URL shortener and webpage archival RESTful web API}}{\href{https://github.com/abhishekarya1/cachemeifyoucan-api}{\underline{link}}}
          \resumeItemListStart
            \resumeItem{Shortened links that redirect to the original, but if the original is down, a cached version of the webpage is displayed. Accessible over a public API to use from the terminal or a separate frontend app.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hashme CLI} $|$ \emph{Command line tool to check file content tampering and corruption}}{\href{https://github.com/abhishekarya1/hashme-cli}{\underline{link}}}
          \resumeItemListStart
            \resumeItem{A handy command-line utility to generate file hashes using the MD5 or SHA256 algorithms to verify file integrity.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ducky Bot} $|$ \emph{Bot to automate posts across social media platforms}}{\href{https://github.com/abhishekarya1/ducky-bot}{\underline{link}}}
          \resumeItemListStart
            \resumeItem{An interactive chat application for the social media app "Discord", offering various options for fetching and posting content asynchronously 
            from Reddit based on user inputs or scheduled posts, along with content filters.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
